Doing a PhD is a long and arduous process, but it is also rewarding and, for the most part, enjoyable.
I have had a great time during my five years at the University of Zurich, in large part due to the people who have been around me.

I have to start with my awesome wife, Dóri, who has been with me every step of the way.
She was always understanding and supportive, from the day I decided to apply for a PhD program to moving to a new country and all the way until the very end.
I am lucky to have her by my side.
The same goes for my daughter, Olivia.
While she was not around for most of the process, she had been a great motivator to finish on time.

I am grateful to my fantastic supervisors, Armin Schmutzler, and Marek Pycia, without whom this dissertation would not have been possible.
Besides their vast knowledge and expertise, they have been amazing mentors, letting me explore my own ideas when I wanted to and providing guidance when I needed it.
I have learned a lot from them and am grateful for the opportunity to work with them.

Many people provided valuable feedback and suggestions on my work.
In particular, I would like to thank Özlem Bedre Defolie and Joao Montez, whose comments helped shape \Cref{ch:application}, and Sandro Ambühl, Nick Netzer, Jakub Steiner, and Roberto A. Weber, who provided thoughtful suggestions about the design of the experiment in \Cref{ch:experiment}.
I am also grateful to the participants of the the Topics in Microeconomic Theory seminar, the Market Design seminar and the Behavioral Lab Meetings at the University of Zurich, as well as the 2023 Swiss IO Day, for their questions and comments.

I would also like to thank my colleagues at the University of Zurich, both faculty members and fellow students.
Being surrounded by such smart people has been a constant source of inspiration.
A special thanks goes to my coauthor, Mia Lu, with whom I have worked on the final chapter of this thesis.
She was not only a great collaborator but also fun to work with.

My family deserves a big thank you for their support and encouragement throughout the years.
I am also grateful to my friends, old and new, with whom we had a great time even when geography made it difficult to meet in person.
We had lots of fun, and I am looking forward to more of it in the future.

Finally, I am also grateful for the financial support I have received from the University of Zurich and the UBS Center of Economics in Society, which has made this dissertation possible.

\vspace{0.5 cm}\hfill Martin Stancsics
