\documentclass[a4paper,11pt]{article}

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb} 
\usepackage{booktabs}
\usepackage[labelsep=period]{caption}
\usepackage{subcaption}
\usepackage[noabbrev,nameinlink]{cleveref}
\usepackage[section]{placeins}
\usepackage{listings}
\usepackage{snapshot}
\usepackage{apptools}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
\usepackage{mfirstuc}

\setstretch{1.15}

\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}

\addbibresource{src/paper/references.bib}
\DeclareFieldFormat{jtnoformat}{\capitalisewords{#1}}

\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/phd-thesis/experiment.pdf}{stanmart.github.io/phd-thesis/experiment.pdf}}}

\DeclareMathOperator*{\argmax}{argmax}

\newtheorem{proposition}{Proposition}

\AtAppendix{\counterwithin{proposition}{section}}
\AtAppendix{\counterwithin{equation}{section}}
\AtAppendix{\counterwithin{figure}{section}}
\AtAppendix{\counterwithin{table}{section}}

\lstset{
    basicstyle=\footnotesize\ttfamily,
    columns=flexible,
    breaklines=true,
}


\title{
    Characterizing Multiplayer Free-Form Bargaining: A Lab experiment%
    \thanks{
        We would like to thank our advisors, Nick Netzer, Marek Pycia, Armin Schmutzler, and Jakub Steiner for their invaluable feedback and support throughout this project.
        We are also grateful to Sandro Ambühl and Roberto A. Weber for the thoughtful suggestions about the design of the experiment.
        Finally, we thank the participants of the Behavioral Lab Meetings and the Market Design Seminar for their questions and comments.
    }
}

\author{
    Mia Lu\thanks{University of Zurich, mia.lu@econ.uzh.ch} 
    \and 
    Martin Stancsics\thanks{University of Zurich, martin.stancsics@econ.uzh.ch}
}

\date{July 30, 2024 \\\vspace{0.4cm} \latestversion}

\begin{document}

\maketitle

\begin{abstract}
    This experiment investigates coalition-formation and surplus division between three players in a free-form bargaining environment.
    We find that players' payoffs are increasing in their bargaining power, but only when forming a smaller coalition and excluding one of the non-monopolist players is a credible threat.
    This is qualitatively consistent with the theoretical predictions of the nucleolus from cooperative game theory, but the observed payoff inequality is significantly lower than the theoretical predictions.
    Our results highlight that fairness considerations seem to play an important role even under free-form bargaining: equal splits make up a large fraction of the outcomes, and fairness-related arguments are used frequently during bargaining.
    We also find considerable heterogeneity between players both in terms of bargaining behavior and stated preferences.
\end{abstract}

\input{src/paper/experiment/body.tex}

\appendix

\printbibliography

\input{src/paper/experiment/appendix.tex}

\end{document}
